---
title: "TermProject"
author: "Julia"
date: "2023-09-26"
output: html_document
---

```{r packages}
library(readr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(RColorBrewer)
library(corrplot)
```

```{r data import}
data <- read_csv("https://raw.githubusercontent.com/hereisjulia/DataScience_MQM/main/TermProject/Loan_default.csv")
```

imputation
change the N/As into avg. (but no nas)


```{r data overview}
str(data)
summary(data)
length(data)
count(data)
```
# Data Cleaning

```{r data}
data_drop <- c("LoanID")
data_clean <- data[, !names(data) %in% data_drop]
data_clean$HasMortgage <- ifelse(data_clean$HasMortgage == "Yes", 1, 0)
data_clean$HasDependents <- ifelse(data_clean$HasDependents == "Yes", 1, 0)
data_clean$HasCoSigner <- ifelse(data_clean$HasCoSigner == "Yes", 1, 0)

education_mapping <- c("High School"= 1, "Bachelor's" = 2, "Master's" = 3, "PhD" = 4)
data_clean$Education <- as.integer(factor(data_clean$Education, levels = names(education_mapping)))

EmploymentType_mapping <- c("Unemployed" = 0, "Self-employed" = 1,"Part-time" = 2, "Full-time" = 3)
data_clean$EmploymentType <- as.integer(factor(data_clean$EmploymentType, levels = names(EmploymentType_mapping)))

MaritalStatus_Mapping <- c("Single" = 0, "Divorced" = 1, "Married" = 2)
data_clean$MaritalStatus <- as.integer(factor(data_clean$MaritalStatus, levels = names(MaritalStatus_Mapping)))

LoanPurpose_mapping <- c("Other" = 0, "Auto" = 1, "Education" = 2, "Home" = 3, "Business" = 4)
data_clean$LoanPurpose <- as.integer(factor(data_clean$LoanPurpose, levels = names(LoanPurpose_mapping)))

length(data_clean)
data_clean
```
### Lasso

```{r chatgpt}
lasso.model <- glmnet(Mx, My, alpha=1)
cv.lasso <- cv.glmnet(Mx, My, alpha=1)
optimal.lambda <- cv.lasso$lambda.min
coef.lasso <- coef(lasso.model, s=optimal.lambda)
selected.variables <- rownames(coef.lasso)[which(coef.lasso[, 1] != 0)]
print(selected.variables)
```

```{r}
library(glmnet)
Mx<- model.matrix(Default ~ ., data=data_clean)[,-1]
My<- data_clean$Default
```


```{r lambda theory}
num.features <- ncol(Mx)
num.n <- nrow(Mx)
num.default <- sum(My)
w <- (num.default/num.n)*(1-(num.default/num.n))
lambda.theory <- sqrt(w*log(num.features/0.05)/num.n)
lassoTheory <- glmnet(Mx,My, family="binomial",lambda = lambda.theory)
summary(lassoTheory)
support(lassoTheory$beta)
colnames(Mx)[support(lassoTheory$beta)]
### there are in total
length(support(lassoTheory$beta))
```

```{r lasso cv}
lassoCV <- cv.glmnet(Mx,My, family="binomial")

plot(lassoCV, main="Fitting Graph for CV Lasso \n \n # of non-zero coefficients  ", xlab = expression(paste("log(",lambda,")")))

optimal_lambda <- lassoCV$lambda.min
lasso_optLambda <- glmnet(Mx,My, family="binomial",lambda = optimal_lambda)
length(support(lasso_optLambda$beta))

coef_matrix <- coef(lasso_optLambda, s = optimal_lambda)
select_variables <- rownames(coef_matrix)[which(coef_matrix != 0)[-1]]
select_variables
# no "LoanTerm"
```

### OOS split
```{r}
set.seed(123456) 
train_indices <- sample(1:nrow(data_clean), 0.8 * nrow(data_clean))
train_data <- data_clean[train_indices, ]
test_data <- data_clean[-train_indices, ]  
```

```{r plot}
ggplot(data=data_clean)+
  geom_col(aes(x = Age, y = Default))
```
Correlation Map
```{r plot}
Corr <- cor(data_clean)
Corr
CorrplotColor <- brewer.pal(n = 8, name = "BrBG")
corrplot(Corr, method = "color",col = CorrplotColor, tl.col = "black")
```

## Models
We want to know whether the customers will defualt on loans, so the outcome should be binary, and this is not a causal question.

Models we can use for this Binary question:

* Logistic Regression
* Decision Trees
* Random Forest
* K-Nearest Neighbors

## Choosing Variables


### logistic regression
```{r}
logisticRegression <- glm(Default~., data = train_data, family = "binomial")
logistic_pred <- predict(logisticRegression, newdata = test_data, type = "response")
logistic_pred <- ifelse(logistic_pred > 0.5, 1, 0)
```

### Decision Trees
```{r}
library(party)
Tree <- ctree(Default~., data = train_data)
Tree_pred <- predict(Tree, newdata = test_data) %>% as.numeric()
Tree_pred <- ifelse(Tree_pred > 0.5, 1, 0)
```


### Random Forest
```{r}
library(randomForest)
train_data$Default <- as.factor(train_data$Default)

randomForest <- randomForest(Default~., data = train_data)
randomForest_pred <- predict(randomForest, newdata = test_data) %>% as.numeric()
```

### Lasso-Logistic
```{r}
logisticRegression_lasso <- glm(Default~.-LoanTerm, data = train_data, family = "binomial")
LassoLogistic_pred <- predict(logisticRegression, newdata = test_data, type = "response")
LassoLogistic_pred <- ifelse(logistic_pred > 0.5, 1, 0)
```


## Evaluation
```{r}
evaluation <- data.frame(
  actual = test_data$Default,
  logistic = logistic_pred,
  tree = Tree_pred,
  randomForest = randomForest_pred
)
# we should use confusion matrix instead
```


confusion matrix (tp, tn)
R2







