---
title: "Case2"
author: "Julia"
date: "2023-09-19"
output: html_document
---

```{r for case 2}
library(readxl)
library(readr)
library(tidyverse)
library(ggplot2)
```

```{r}
data <- read_csv("./Case2/ALLSTATEcost.csv")
summary(data)
```
# Task Description

To predict competitior's quotes by the given data.
(Analyze what is their pricing strategy.)

Target Variable: cost

`customer_ID` - A unique identifier for the customer
`shopping_pt` - Unique identifier for the shopping point of a given customer - 地點
`record_type` - 0=shopping point, 1=purchase point
`day` - Day of the week (0-6, 0=Monday)
`time` - Time of day (HH:MM)
`state` - State where shopping point occurred
`location` - Location ID where shopping point occurred
`group_size` - How many people will be covered under the policy (1, 2, 3 or 4)
`homeowner` - Whether the customer owns a home or not (0=no, 1=yes)
`car_age` - Age of the customer’s car
`car_value` - How valuable was the customer’s car when new
`risk_factor` - An ordinal assessment of how risky the customer is (1, 2, 3, 4 or NA)
`age_oldest` - Age of the oldest person in customer's group
`age_youngest` - Age of the youngest person in customer’s group
`married_couple` - Does the customer group contain a married couple (0=no, 1=yes)
`C_previous` - What the customer formerly had or currently has for product option C
(0=nothing, 1, 2, 3,4 or NA)
`duration_previous` - how long (in years) the customer was covered by their previous
issuer (duration or NA)
A,B,C,D,E,F,G - the coverage options: 
`A` = Collision (levels: 0, 1, 2); 
`B` = Towing (levels: 0, 1); 
`C` = Bodily Injury (BI, levels: 1, 2, 3, 4); 
`D` = Property Damage (PD, levels 1, 2, 3); 
`E` = Rental Reimbursement (RR, levels: 0, 1); 
`F` = Comprehensive (Comp, levels: 0, 1, 2, 3);
`G` = Medical/Personal Injury Protection (Med/PIP, levels: 1, 2, 3, 4)



















